MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-21 ms.tex
added caption for HOG and first major summary point

Figure ~\ref{fig:mockimages} illustrates a sample mock lensed and
unlensed images from each telescope.  From left to right, the top
panel images respectively correspond to a mock HST lensing and
non-lensing system. The mock HST images are $n_\text{pix}\times
n_\text{pix}=300\times300$ in size.  For the HST-like dataset, many
giant arcs are visually obvious.

The bottom panel images respectively correspond to a mock LSST lensing
and non-lensing system.  These images are $n_\text{pix}\times
n_\text{pix}=45\times45$.  The ground based noise and limited
resolution of the LSST-like dataset make visual giant arc
identification difficult.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  The brightest lines align with
  prominent edges.  Note, while fewer pixels per cell will better
  resolve the arc feature, the ``edge'' corresponding to the arc is
  less prominent.  }
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item Publicly released pipeline will be... swap out feature
  extraction, machine learning algorithm, perform parameter searches,
  and train a model with best parameters.

>>>>

Figure ~\ref{fig:mockimages} illustrates a sample mock lensed and
unlensed images from each telescope.  The top left and right panel
images respectively correspond to a mock HST lensing and non-lensing
system. The mock HST images are $n_\text{pix}\times
n_\text{pix}=300\times300$ in size.  For the HST-like dataset, many
giant arcs are visually obvious.

The middle row corresponds to the same simulated systems, as observed
with a single epoch of LSST.  These images are $n_\text{pix}\times
n_\text{pix}=45\times45$.  The ground based noise and limited
resolution of the LSST-like dataset make visual giant arc
identification difficult.  However, by stacking observations over the
course of the LSST survey, we recover the arc feature, albeit at a
much lower resolution than with the HST-like image. The bottom row
shows the mock stacked observation, where the lensed background galaxy
is now visible.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1or4ppc3cpb3.pdf}\hspace{-20pt}
%\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1or4ppc3cpb3.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1or4ppc3cpb3.pdf}
%\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1or4ppc3cpb3.pdf}
\caption{Top row: Visualized HOG feature vectors of the sample lensed
  HST-like image from Figure~\ref{fig:mockimages}.  Left: The
  corresponding HOG visualization with N$_\text{orient}=5$, (32, 32)
  pixels per cell, and (1, 1) cells per block.  Right: The HOG
  visualization of the same mock image with N$_\text{orient}=9$, (16,
  16) pixels per cell, and (1, 1) cells per block.  The brightest
  lines align with prominent edges.  Note, while fewer pixels per cell
  will better resolve the arc feature, the ``edge'' corresponding to
  the arc is less prominent.  Bottom row: Visualized HOG feature
  vectors for the LSST-like single epoch and stacked images with the
  best scoring HOG parameterization of N$_\text{orient}=4$, (3, 3)
  pixels per cell, and (3, 3) cells per block.  The single epoch image
  (left) does not have significant enough edge features to emerge in
  the HOG, but the stacked image (right) does.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item We have designed our pipeline to easily select and add image
  pre-processing and feature extraction methods, and to select a
  machine learning algorithm for classification.  Additionally, the
  user can easily perform parameter searches, and train a model with
  best parameters.
